Model-theoretic aspects of relativised cylindric set algebras

### 2020-10-15 problem-19.17/FRP.tex
cylindric stuff: atom structures and canonical extensions

\begin{theorem}\label{ors=irrs}
  ${\bf ORS} = {\bf IRRS}$, where ${\bf IRRS}$ is a closure of ${\bf RRS}$ under isomorphic copies.
\end{theorem}
One may reformulate this result as $\mathcal{A} \in {\bf R}(;, \setminus, /, \leq)$ iff $\mathcal{A}$ is a residuated semigroup.

@@

In \cite{hirsch2002relation}, Hirsch and Hoskidson left the problem about having the finite representation property. Given a finite algebra $\mathcal{A} \in {\bf RRS}$, we show that $\mathcal{A}$ is isomorphic to some algebra $\mathcal{B}$ that has the finite base.

First of all, let us show that
\begin{lemma} \label{rrsLemma}
  Let $\mathcal{A} = \langle A, \cdot, \setminus, /, \leq \rangle$ be a residuated semigroup, then its representation with relational quantales belongs to ${\bf RRS}$.
\end{lemma}

\begin{proof}
  By Corollary~\ref{orsRep2}, $\mathcal{A}$ is isomorphic subalgebra of $\widehat{\mathcal{Q}_{\mathcal{A}}}$, where
  $\widehat{\mathcal{Q}_{\mathcal{A}}} = \langle R, ;, \bigvee \rangle$ is a quantale of Theorem~\ref{orsRep}.
  $\mathcal{Q}_{\mathcal{A}}$ is the quantale of Galois stable subsets of $\mathcal{A}$.

@@

Let us put $\tau = \{ ;, {\bf 1} \}$. Recall that $\mathcal{A} \in {\bf R}(\tau)$ iff $\mathcal{A} = \langle A, ;, {\bf 1} \rangle$ is a monoid. That is, every monoid is representable. The finite representation property for finite monoids might be shown with a Cayley representation putting $A$ as a base set and defining:
\begin{center}
  $a^R = \{ (b, b ; a) \: | \: b \in A \}$
\end{center}
Thus, we have
\begin{lemma}
  Let $\tau \subseteq \{ ;,  \}$ ${\bf R}(\tau)$ has the finite representation property.
\end{lemma}

@@

In contrast to usual monoids, the universal theory of representable partially ordered monoids is not finitely axiomatisable \cite{hirsch2005class}.

\begin{lemma}
  ${\bf R}(;, {\bf 1}, \leq)$ has (?) the finite representation property.
\end{lemma}

\begin{proof}

\end{proof}

\begin{theorem}
  ${\bf R}(;, \setminus, /, {\bf 1}, \leq)$ has (?) the finite representation property.
\end{theorem}

>>>>

\begin{theorem}\label{ors=irrs}
  ${\bf ORS} = {\bf IRRS}$, where ${\bf IRRS}$ is a closure of ${\bf RRS}$ under isomorphic copies.
\end{theorem}
One may reformulate this result as $\mathcal{A} \in {\bf R}(;, \setminus, /, \leq)$ iff $\mathcal{A}$ is a residuated semigroup. Thus, it is sufficient to show that any finite residuated semigroup has a representation over a finite base.

@@

Hirsch and Hoskidson left the problem about having the finite representation property. Given a finite algebra $\mathcal{A} \in {\bf RRS}$, we show that $\mathcal{A}$ is isomorphic to some algebra over a finite base.

First of all, let us show that
\begin{lemma} \label{rrsLemma}
  Let $\mathcal{A} = \langle A, \cdot, \setminus, /, \leq \rangle$ be a residuated semigroup, then its representation with relational quantales belongs to ${\bf RRS}$.
\end{lemma}
\begin{proof}
  By Corollary~\ref{orsRep2}, $\mathcal{A}$ is isomorphic subalgebra of $\widehat{\mathcal{Q}_{\mathcal{A}}}$, where
  $\widehat{\mathcal{Q}_{\mathcal{A}}} = \langle R, ;, \bigvee \rangle$ is a quantale of Theorem~\ref{orsRep}.
  $\mathcal{Q}_{\mathcal{A}}$ is the quantale of Galois stable subsets of $\mathcal{A}$.

@@

Let us put $\tau = \{ ;, {\bf 1} \}$. Recall that $\mathcal{A} \in {\bf R}(\tau)$ iff $\mathcal{A} = \langle A, ;, {\bf 1} \rangle$ is a monoid. That is, every monoid is representable. The finite representation property for finite monoids might be shown with a Cayley representation putting $A$ as a base set and defining:
\begin{center}
  $a^R = \{ (b, b ; a) \: | \: b \in A \}$
\end{center}
Thus, we have
\begin{lemma}
  Let $\tau \subseteq \{ ;, \leq \}$, then ${\bf R}(\tau)$ has the finite representation property.
\end{lemma}

@@

It is known that $\mathcal{A} \in {\bf R}(;, \leq)$ iff $\mathcal{A}$ is an ordered semigroup \cite{zaretskii1959representation} and the class ${\bf R}(;, \leq)$ is finitely axiomatisable.

In contrast to usual monoids, the universal theory of representable partially ordered monoids is not finitely axiomatisable \cite{hirsch2005class}. However, the universal theory of representable residuated monoids coincide with the theory of the whole class of residuated monoids and, thus, is finitely axiomatisable \cite{andreka1994lambek}. Let us recall how the uniform representation for residuated monoids looks like. In fact, we reproduce the proof sketch of Theorem~\ref{ors=irrs} assuming that a given algebra is finite.

\begin{defin}
  A network
\end{defin}

TODO: a desired network

TODO: inductive steps in a nutshell

TODO: an interpretation

TODO: extract the finite base from a representation

\begin{theorem}
  ${\bf R}(;, \setminus, /, {\bf 1}, \leq)$ has the finite representation property.
\end{theorem}

### 2020-10-15 problem-9.4/Text.tex
a small cylindric update
update
wip: rainbow construction for R(;, \vee)
cylindric stuff: atom structures and canonical extensions

@@

@@

Let $A$ be a non-empty set, an \emph{ultrafilter} on $A$ is a set of subsets $U \subseteq \mathcal{P}(\mathcal{P})(A)$ such that $A$ is closed under intersections, $\subseteq$-upwardly closed, and either $X \in U$ or $- X \in U$, where $X \subseteq A$. An ultrafilter is called principal if it has the form $\uparrow X = \{ Y \in \mathcal{P}(A) \: | \: X \subseteq Y \}$.

Let $\Omega = \langle \operatorname{Cnst}, \operatorname{Fn}, \operatorname{Pred} \rangle$ be a signature and $\Lambda$ an index set, and let $\{ M_{\lambda}\}_{\lambda \in \Lambda}$ be an indexed set of $\Omega$ structures. The $\Omega$-structure
\begin{center}
  $M = \prod \limits_{\lambda \in \Lambda} M_{\lambda}$
\end{center}
is called a \emph{product} that defined as follows. Its domain is the Cartesian product of the domains of $M_{\lambda}$. $a \in M$ is a function $\Lambda \to \bigcup \limits_{\lambda \in \Lambda} \operatorname{dom}(M_{\lambda})$ such that $a(\lambda) \in M_{\lambda}$ for each $\lambda \in \Lambda$.
Given $\lambda \in \Lambda$ and $a_{\lambda} \in M_{\lambda}$, we denote the function mapping $\lambda$ to $a_{\lambda}$ as
$\langle a_{\lambda} \: | \: \lambda \in \Lambda \rangle$. We define the interpretation of $\Omega$-symbols as

\begin{enumerate}
  \item If $c \in \operatorname{Cnst}$, then $c^{M} = \langle c^{M_{\lambda}} \: | \: \lambda \in \Lambda \rangle$
  \item If $f \in \operatorname{Fn}$ is an $n$-ary function symbol, then $f^{M}(\overline{a}) = \langle f^{M_{\lambda}}(\overline{a}) \: | \: \lambda \in \Lambda \rangle$, where $\overline{n} \in M^{n}$
  \item If $R \in \operatorname{Pred}$ is an $n$-ary relation symbol and $\overline{n} \in M^{a}$, then $R^{M}(\overline{a}) = \langle R^{M_{\lambda}}(\overline{a}) \: | \: \lambda \in \Lambda \rangle$
\end{enumerate}

Given $\lambda \in \Lambda$, we define the $\lambda$th projection as $\pi_{\lambda} : M \to M_{\lambda}$ such that $\pi_{\lambda}(a) = a(\lambda)$.

@@

\subsection{Preliminaries from universal algebra}

\begin{defin}
  Let ${\bf K}$ be a class of $\Omega$-structures, then ${\bf K}$ is a variety, if it is defined by some set of equations.
  The variety generated by ${\bf K}$ is the smallest variety contatining ${\bf K}$. ${\bf K}$ is a quasi-variety, if it is defined by some
  set of quasi-identities.
\end{defin}

Given a class ${\bf K}$ of $\Omega$-structures, then ${\bf I}({\bf K})$, ${\bf S}({\bf K})$, ${\bf H}({\bf K})$, and ${\bf P}({\bf K})$ are
the classes of isomorphic copies, algebras isomorphic to subalgebras belonging to ${\bf K}$,
algebras isomorphic to homomorphic images belonging to ${\bf K}$, and algebras isomorphic to direct products belonging to ${\bf K}$.
We claim that ${\bf I}({\bf K}) \subseteq {\bf S}({\bf K})$. ${\bf Up}({\bf K})$ is the class of algebras isomorphic to ultraproducts
belonging to ${\bf K}$.

\begin{theorem} Let ${\bf K}$ be a class of $\Omega$-structures

  \begin{enumerate}
    \item ${\bf K}$ is a variety iff ${\bf H}({\bf K}), {\bf S}({\bf K}), {\bf P}({\bf K}) \subseteq {\bf K}$
    \item ${\bf HSP}({\bf K}) = {\bf H}({\bf S}({\bf P}({\bf K})))$ is the smallest variety containg ${\bf K}$
    \item ${\bf K}$ is a quasi-variety iff it is closed under subalgebras, products, and ultraproducts, iff ${\bf SPUp}({\bf K}) = {\bf K}$.
  \end{enumerate}
\end{theorem}

\subsection{Subdirect products}

  \begin{enumerate}
    \item Let $\{ A \}_{i \in I}$ be $\Omega$-structures, a subdirect product of $\langle A_i \: | \: i \in I \rangle$ is a
    subalgebra $B$ of $\prod \limits_{i \in I} A_i$ such that for each $i \in I$, a projection map $\pi_i : B \to A_i$ is a surjection.
    \item A subdirect representation of an $\Omega$-structure is an embedding $f : A \to \prod \limits_{i \in I} A_i$ for some $I$ and
    $\{ A_i \}_{i \in I}$ such that $f \circ \pi_i : A \to A_i$ is a surjection.
    \item An $\Omega$-structure $A$ is subdirectly irreducible if for every subdirect representation $f : A \to \prod \limits_{i \in I} A_i$
    there exists a projection $\pi_i$ such that $f \circ \pi_i$ is an isomorphism.
    \item ${\bf Sir}({\bf K})$ is the class of subdirectly irreducible structures belonging to ${\bf K}$.
    \item A subdirect decomposition of $A$ if there exists a subdirect representation $f : A \to \prod \limits_{i \in I} A_i$ such that
    every $A_i$ is subdirectly irreducible.
  \end{enumerate}
\end{defin}

It is known that every Boolean algebra with operators has a subdirect demcomposition. Moreover, that implies:
\begin{theorem}
$ $

  \begin{enumerate}
  \item If ${\bf K}$ is a variety, then every element of ${\bf K}$ has a subdirect decomposition with some subdirect irreducible elements of
  ${\bf K}$.
  \item If ${\bf K}$ is a variety and $\varepsilon$ is an equation,
  ${\bf Sir}({\bf K}) \models \varepsilon \Leftrightarrow {\bf K} \models \varepsilon$.
\end{enumerate}
\end{theorem}

\subsection{Pseudo-elementary classes}

\section{Cylindric algebras}

  \begin{enumerate}
    \item A subset of $U^{\alpha}$ is an $\alpha$-ry relation on $U$. For $i, j < \alpha$, the $i,j$-diagonal $D_{ij}$ is the set of all
    elements of $U$ such that $y_i = y_j$. If $i < \alpha$ and $X$ is an $\alpha$-ry relation on $U$, then
    the $i$-th cylindrification $C_i X$ is the set of all elements of $U$ that agree with some element of $X$ on each coordinate except the
    $i$-th one. To be more precise,
    $C_i X = \{ y \in U^{\alpha} \: | \: \exists x \in X \forall i < \alpha \: (i \neq j \Rightarrow y_j = x_j)\}$.
    \item A cylindic set algebra of dimension $\alpha$ is an algebra consisting of a set $S$ of $\alpha$-ry relation on some base set $U$
    with the constants and operations $0 = \emptyset$, $1 = U^{\alpha}$, $\cap$, $-$, the diagonal elements $\{ D_{ij} \}_{i, j < \alpha}$,
    the cylindrifications $\{ C \}_{i < \alpha}$. A generalised cylindric set algebra of dimension $\alpha$ is a subdirect of
    cylindric algebras that have dimension $\alpha$
    \item A cylindric algebra of dimension $\alpha$ is an algebra $\mathcal{C} = \langle \mathcal{B}, \{ c_i \}_{i < \alpha}, \{ d_{ij} \}_{i, j < \alpha} \rangle$ such that
    \begin{itemize}
      \item $\mathcal{B}$ is a Boolean algebra, for each $i, j < \alpha$ $c_i$ is an operator and $d_{ij} \in \mathcal{B}$
      \item For each $i < \alpha$, $a \leq c_i a$, $c_i (a \land c_i b) = c_i a \land c_i b$ and $d_{ii} = 1$
      \item For every $i, j < \alpha$, $c_i c_j a = c_j c_i a$
      \item If $k \neq i, j < \alpha$, then $d_{ij} = c_k (d_{ij} \land d_{jk})$
      \item If $i \neq j$, then $c_i (d_{ij} \land a) \land c_i (d_{ij} \land - a) = 0$
    \end{itemize}
    ${\bf CA}_{\alpha}$ is the class of all cylindric algebras of dimension $\alpha$
    \item An $\alpha$-dimensional cylindric algebra $C$ is representable, if it is isomorphic to a generalised cylindric set algebra
    of dimension $\alpha$. Such is isomorphism is a representation of $C$.
    ${\bf RCA}_{\alpha}$ is the class of all representable cylindric algebras that have dimension $\alpha$.
  \end{enumerate}
\end{defin}

@@

\section{${\bf IG}_{\omega}$ is (not) a variety; is (not) (pseudo-)elementary}

>>>>

\theoremstyle{fact}
\newtheorem{fact}{Fact}

@@

\section{The problems themselves}

\begin{enumerate}
\item Suppose $\mathcal{C} \in {\bf RCA}_{\omega}$, whether $\mathcal{C}$ has a complete, $\omega$-dimensional representation?
\item Is the class ${\bf IG}_{\omega}$ (the isomorphism-closure of the $\omega$-dimensional cylindric relativised set algebras in which the unit is closed under substitutions and permutations) a variety, or even
a pseudo-elementary class? Is it closed under ultraproducts?
\end{enumerate}

\section{Boolean algebras with operators and cylindric algebras}

\begin{defin}

$ $

  \begin{enumerate}
    \item Let $\mathcal{B} = \langle B, +, -, 0, 1 \rangle$ be a Boolean algebra. An operator is an $n$-ary function $\Omega : B^n \to B$ satisfying the following conditions:
    \begin{itemize}
      \item Normality: for all $b_0, \dots, b_{n - 1} \in B$, if $b_1 = 0$ for some $i < n$, then

\begin{center}
      $\Omega(b_0, \dots, b_{i - 1}, 0, b_{i+1}, \dots, b_{n - 1}) = 0$
\end{center}
      \item Additivity: for all $b_0, \dots, b_{n - 1}, b, b' \in B$ we have
      \begin{center}
        $\Omega(b_0, \dots, b_{i - 1}, (b + b'), b_{i+1}, \dots, b_{n - 1}) = \Omega(b_0, \dots, b_{i - 1}, b, b_{i+1}, \dots, b_{n - 1}) + \Omega(b_0, \dots, b_{i - 1}, b', b_{i+1}, \dots, b_{n - 1})$
      \end{center}
    \end{itemize}
    \item Let $I$ be an index set, a Boolean algebra with operators (BAO) is an algebra $\langle B, +, -, 0, 1, \{ \Omega_{i} \}_{i \in I} \rangle$ such that $\langle B, +, -, 0, 1 \rangle$ is a Boolean algebra and for each $i \in I$ $\Omega_{i}$ is an operator.
  \end{enumerate}
\end{defin}

\begin{defin} Let $\mathcal{B} = \langle B, +, -, 0, 1, \{ \Omega_{i} \}_{i \in I} \rangle$ be a BAO, then

  \begin{enumerate}
    \item An opetator $\Omega$ is completely additive, if for each $b_0, \dots, b_{n - 1} \in B$ and $X \subseteq B$, one has

    \begin{center}
      $\Omega(b_0, \dots, b_{i-1}, \sum X, b_{i+1}, \dots, b_{n - 1}) = \sum \limits_{x \in X} \Omega(b_0, \dots, b_{i-1}, x, b_{i+1}, \dots, b_{n - 1})$
    \end{center}
    \item $\mathcal{B}$ is completely additive, if for each $i \in I$ $\Omega_{i}$ is additive,
    \item A class $\mathcal{K}$ of BAOs is completely additive, if every $\mathcal{B} \in \mathcal{K}$ is completely additive.
  \end{enumerate}
\end{defin}

\subsection{Atom structures and canonical extensions}

\begin{defin}  Let $I$ be an index set and $\{ \Omega_i\}_{i \in I}$ a set of function symbols
\begin{enumerate}
  \item An atom structure is a relational structrure
  $\mathcal{F} = \langle W, \{ R_{i} \}_{i \in I} \rangle$
  such that $R_{i}$ is a $n+1$-ary relation symbol, if $\Omega_{i \in I}$ is an $n$-ary function symbol,
  \item Let $\mathcal{B}$ be an atomic BAO of the signature $I$,
the atom structure of $\mathcal{B}$, written as ${\bf At} \mathcal{B}$, is an atom structure $\langle \operatorname{At}(\mathcal{B}), \{ R_{i}\}_{i \in I} \rangle$ such that for each
$a, b_0, \dots, b_{n + 1} \in \operatorname{At}(\mathcal{B})$ and for each $i \in I$
\begin{center}
  ${\bf At} \mathcal{B} \models R_{i}(a,  b_0, \dots, b_{n + 1})$ iff $\mathcal{B} \models a \leq \Omega_{i}(b_0, \dots, b_{n + 1})$
\end{center}
\item Let $\mathcal{F} = \langle W, \{ R_{i} \}_{i \in I} \rangle$ be an atom structure, the complex algebra of $\mathcal{F}$, written as $\bf{Cm} \mathcal{F}$, is a BAO
$\langle \mathcal{P}(W), \cup, -, \emptyset, W, \{\Omega_{R_{i}}\}_{i \in I} \rangle$ such that
for all $X_0, \dots, X_{n - 1} \subseteq W$ and for each $i \in I$
\begin{center}
  $\Omega_{R_{i}}(X_0, \dots, X_{n - 1}) = \{ a \in W \: | \: \exists b_0 \in X_0 \dots \exists b_{n -1} \in X_{n - 1} \: \mathcal{F} \models R_{i}(a, b_0, \dots, b_{n - 1})\}$
\end{center}
\end{enumerate}
\end{defin}

The following duality is due to Thomason \cite{thomason1975categories}.

\begin{fact}
  $ $

  \begin{enumerate}
    \item Let $\mathcal{B}$ be a complete atomic BAO, then $\mathcal{B} \cong \bf{Cm} (\bf{At}(\mathcal{B}))$,
    \item Let $\mathcal{F}$ be an atom structure, then $\mathcal{F} \cong {\bf At}({\bf Cm}(\mathcal{B}))$.
  \end{enumerate}
\end{fact}

Let $A$ be a non-empty subset of a Boolean algebra $\mathcal{B}$, $A$ is a \emph{filter}, if $A$ is closed under finite infima and upwardly closed. $A$ is an ultrafilter, if it has no non-trivial extensions. That is, if $A \subseteq A'$, then $A' = \mathcal{B}$.

\begin{defin}
  Let $\mathcal{B} = \langle B, +, -, 0, 1, \{ \Omega_i \}_{i \in I} \rangle$ be a BAO and ${\bf Uf}(\mathcal{B})$ the set of its ultrafilters. The ultrafilter frame of $\mathcal{B}$ (or canonical frame) is a relational structure $\mathcal{F}_{\mathcal{B}} = \langle {\bf Uf}(\mathcal{B}), R_{\Omega_i} \rangle$ such that for each ultrafilters $\beta_0, \dots, \beta_{n - 1}, \gamma$ one has
  \begin{center}
    ${\bf Uf}(\mathcal{B}) \models R_{\Omega_i}(\beta_0, \dots, \beta_{n - 1}, \gamma)$ iff $\{ \Omega(b_0, \dots, b_{n - 1}) \: | \: b_0 \in \beta_0, \dots, b_{n - 1} \in \beta_{n - 1}\} \subseteq \gamma$.
  \end{center}
\end{defin}

\begin{defin} Let $\mathcal{B}$ be a BAO, then

  \begin{enumerate}
    \item The canonical extension of $\mathcal{B}$ is a complex algebra of the canonical frame ${\bf Cm}(\mathcal{F}_{\mathcal{B}})$ denoted as $\mathcal{B}^{+}$,
    \item The class of BAOs is canonical, if it is closed under canonical extensions.
  \end{enumerate}
\end{defin}

\begin{theorem} Let $\mathcal{A}$, $\mathcal{B}$ be BAOs,

\begin{enumerate}
  \item There exists $\iota : \mathcal{A} \hookrightarrow \mathcal{A}^{+}$ such that
  $\iota : a \mapsto \{ \gamma \in {\bf Uf}(\mathcal{A}) \: | \: a \in \gamma \}$.
  \item If $i : \mathcal{A} \hookrightarrow \mathcal{B}$, then this embedding might be extented to the embedding
  $i^{+} : \mathcal{A}^{+} \hookrightarrow \mathcal{B}^{+}$
\end{enumerate}
\end{theorem}

\begin{fact}
\end{fact}

  \begin{enumerate}
    \item A subset of $U^{\alpha}$ is an $\alpha$-ry relation on $U$. For $i, j < \alpha$, the $i,j$-diagonal $D_{ij}$ is the set of all
    elements of $U$ such that $y_i = y_j$. If $i < \alpha$ and $X$ is an $\alpha$-ry relation on $U$, then
    the $i$-th cylindrification $C_i X$ is the set of all elements of $U$ that agree with some element of $X$ on each coordinate except the
    $i$-th one. To be more precise,
    $C_i X = \{ y \in U^{\alpha} \: | \: \exists x \in X \forall i < \alpha \: (i \neq j \Rightarrow y_j = x_j)\}$.
    \item A cylindic set algebra of dimension $\alpha$ is an algebra consisting of a set $S$ of $\alpha$-ry relation on some base set $U$
    with the constants and operations $0 = \emptyset$, $1 = U^{\alpha}$, $\cap$, $-$, the diagonal elements $\{ D_{ij} \}_{i, j < \alpha}$,
    the cylindrifications $\{ C \}_{i < \alpha}$. A generalised cylindric set algebra of dimension $\alpha$ is a subdirect of
    cylindric algebras that have dimension $\alpha$
    \item A cylindric algebra of dimension $\alpha$ is an algebra $\mathcal{C} = \langle \mathcal{B}, \{ c_i \}_{i < \alpha}, \{ d_{ij} \}_{i, j < \alpha} \rangle$ such that
    \begin{itemize}
      \item $\mathcal{B}$ is a Boolean algebra, for each $i, j < \alpha$ $c_i$ is an operator and $d_{ij} \in \mathcal{B}$
      \item For each $i < \alpha$, $a \leq c_i a$, $c_i (a \land c_i b) = c_i a \land c_i b$ and $d_{ii} = 1$
      \item For every $i, j < \alpha$, $c_i c_j a = c_j c_i a$
      \item If $k \neq i, j < \alpha$, then $d_{ij} = c_k (d_{ij} \land d_{jk})$
      \item If $i \neq j$, then $c_i (d_{ij} \land a) \land c_i (d_{ij} \land - a) = 0$
    \end{itemize}
    ${\bf CA}_{\alpha}$ is the class of all cylindric algebras of dimension $\alpha$
    \item An $\alpha$-dimensional cylindric algebra $C$ is representable, if it is isomorphic to a generalised cylindric set algebra
    of dimension $\alpha$. Such is isomorphism is a representation of $C$.
    ${\bf RCA}_{\alpha}$ is the class of all representable cylindric algebras that have dimension $\alpha$. In particular, we are interested in the case when $\alpha = \omega$.
  \end{enumerate}
\end{defin}

@@

@@

@@

\section{${\bf IG}_{\omega}$ is (not) (pseudo-)elementary; is (not) a variety}
